Landscape heterogeneity simulation figures

### 2018-01-24 Manuscript_figures_2017_12_12.Rmd
Remove computer-specific setwd()

```{r}
setwd("C:/Users/law2y/OneDrive/R Code/IBM/August 2017")
merged_data<-read.csv("IBMsummary.csv")
merged_data<-merged_data[-which(merged_data$beta2==5),] #remove saturating beta_2 values

@@

#Set working directory of where to produce Figures
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
```

@@

##Figure 1
Representation of neutral landscapes
```{r}
#' Create neutral landscape maps
library(raster)

@@

##Figure 2
Random forest variable importance results
```{r}
library(randomForest)
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Random Forest Analysis")

@@

setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
tiff("Fig2_RF.tif", height =16 , width =8.7, units = "cm", compression = "lzw", res = 300)
multiplot(A, B, C, cols=1)
dev.off()

@@

##Figure 3
Box plots rec rate vs. density
```{r}
setwd("C:/Users/law2y/OneDrive/R Code/LandscapeCh/Figures Dec. 2017")
sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks

@@

##Figure 4
```{r}
#percep=3, rec_rate=0.2, density=0.5
p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=max_prevalence, fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii

@@

##Figure 4 (log version)
```{r}
#percep=3, rec_rate=0.2, density=0.5
p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(max_prevalence), fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Maximum prevalence)", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii

@@

##Figure 5
```{r}
#percep=3, rec_rate=0.1, density=0.5
p3r0.1d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.1 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=max_prevalence,fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii

@@

##Figure 5 (log version)
```{r}
#percep=3, rec_rate=0.1, density=0.5
p3r0.1d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.1 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=log(max_prevalence),fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Maximum prevalence)", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii

@@

##Figure 6
Comparing effects on landscape structure for a single RSF(\beta_1=6, \beta_2=2, \beta_3=-0.5) for different densities, perceptual distances, and recovery rates.
```{r}
sub_data<-merged_data[which(merged_data$max_I>1),]

@@

##Supplementary Figure 7
Box plot of percep vs. rec rate vs. density
```{r}
sub_data<-merged_data[which(merged_data$max_I>1),]

@@

tiff("FigureS7.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(gg,hh, cols=1)
dev.off()

@@

##Supplementary Figure 8 (Heat map)
Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing rec rates 0.1 and 0.2
```{r}
r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.5),]

@@

tiff("FigureS8_heatmap.tiff", height = 18, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(hh,gg, ii,jj, cols=1)
dev.off()
```

#Supplement beta2/beta3
```{r}
#Function to calculate rsf
myrsf=function(x,b1,b2) exp(x*b1+x^2*b2)   #caclulate rsf

>>>>

```{r}
#Set working directory to where IBMsummary.csv is located
#setwd()
merged_data<-read.csv("IBMsummary.csv")
merged_data<-merged_data[-which(merged_data$beta2==5),] #remove saturating beta_2 values

@@

#Set working directory of where to produce Figures
#setwd()
```

@@

## Figure 1
Representation of neutral landscapes
```{r}
#' Create neutral landscape maps
library(raster)

@@

## Figure 2
Random forest variable importance results
```{r}
library(randomForest)
#setwd()

@@

#setwd()
tiff("Fig2_RF.tif", height =16 , width =8.7, units = "cm", compression = "lzw", res = 300)
multiplot(A, B, C, cols=1)
dev.off()

@@

## Figure 3
Box plots rec rate vs. density
```{r}
#setwd()
sub_data<-merged_data[which(merged_data$max_I>1),] #successful outbreaks

@@

## Figure 4
```{r}
#percep=3, rec_rate=0.2, density=0.5
p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=max_prevalence, fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii

@@

## Figure 4 (log version)
```{r}
#percep=3, rec_rate=0.2, density=0.5
p3r0.2d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.2 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.2d0.5, aes(x=betas, y=log(max_prevalence), fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Maximum prevalence)", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii

@@

## Figure 5
```{r}
#percep=3, rec_rate=0.1, density=0.5
p3r0.1d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.1 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=max_prevalence,fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "Maximum prevalence", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii

@@

## Figure 5 (log version)
```{r}
#percep=3, rec_rate=0.1, density=0.5
p3r0.1d0.5<-merged_data[which(merged_data$percep==3 & merged_data$rec_rate==0.1 & merged_data$density==0.5),]
ii<- ggplot(data=p3r0.1d0.5, aes(x=betas, y=log(max_prevalence),fill=as.factor(beta2)))
ii<- ii+ geom_boxplot()+ facet_grid( p~ H)
ii<- ii+ labs(x = expression(RSF~(beta[1]~beta[2]~beta[3])), y = "ln(Maximum prevalence)", title="(A)", fill= expression(beta[2]))
ii<- ii+ theme(axis.title = element_text(face="bold", size=20))
ii<- ii + theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0, size=16))
ii<- ii + theme(axis.text.y = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(strip.text = element_text(vjust=0.5, size=16)) 
ii<- ii + theme(legend.text = element_text(vjust=0.5, size=16), legend.title=element_text(vjust=0.5, size=18))
ii<- ii + geom_vline(xintercept=c(6.5,12.5), linetype="dashed")
ii

@@

## Figure 6
Comparing effects on landscape structure for a single RSF(\beta_1=6, \beta_2=2, \beta_3=-0.5) for different densities, perceptual distances, and recovery rates.
```{r}
sub_data<-merged_data[which(merged_data$max_I>1),]

@@

## Supplementary Figure 2
Box plot of percep vs. rec rate vs. density
```{r}
sub_data<-merged_data[which(merged_data$max_I>1),]

@@

tiff("FigureS2.tiff", height = 11.5, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(gg,hh, cols=1)
dev.off()

@@

## Supplementary Figure 3 (Heat map)
Heatmap of max prevelance and mean duration for conspecific density=0.5 and comparing rec rates 0.1 and 0.2
```{r}
r2<-merged_data[which(merged_data$rec_rate==0.2 & merged_data$density==0.5),]

@@

tiff("FigureS3_heatmap.tiff", height = 18, width = 14, units = "in", compression = "lzw", res = 300)
multiplot(hh,gg, ii,jj, cols=1)
dev.off()
```

## Supplementary Figure 1 
Calibrate beta1/beta2/beta3
```{r}
#Function to calculate rsf
myrsf=function(x,b1,b2) exp(x*b1+x^2*b2)   #caclulate rsf
